---
title: 'Assignment 2: Exploratory Data Analysis'
author: Naveen
date: '2021-06-18'
slug: assignment-2-exploratory-data-analysis
categories:
  - ggplot2
tags: []
---



```{r packages, echo = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
library(ggtext)
library(knitr)
library(kableExtra)
set.seed(1234)
options(dplyr.print_min = 10, dplyr.print_max = 6)
```


# Assignment 2: Exploratory Data Analysis

Naveen Kapoor


# The World Bank Data Economy And Growth

This data set has been taken from the World Bank and it talks about the growth of economy from last 50 years. I have chosen this dataset because I have seen due to pandemic lot of countries have been affected by the stalled growth at each sector. I have taken this dataset from: https://github.com/ZeningQu/World-Bank-Data-by-Indicators/tree/master/economy-and-growth

```{r warning = FALSE, message=FALSE, echo = FALSE}
library(tidyverse)
wbdata <- read_csv("economy-and-growth.csv")


```


# Initial Analysis Questions

1. Analysis of exports of goods and services.
2. How foreign direct investment impacted?
3. How transport services impacted over the years?
4. Analysis of export of ICT Services.


# Discoveries & Insights

Export Of Good and Services from 1960 to 2018

```{r height-width-plot, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(data = wbdata, aes(x = Year, y = Exportsofgoodsandservices)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "#8E2C90") + 
  labs(
    title = "Year vs. Export of Goods (Dollars)",
    subtitle = "Export Of Goods, 1960 - 2018",
    x = "Width (Years)",
    y = "Height (Dollar)"
  )

```

## Foriegn Direct Investment over the year

```{r vis-res-3, echo = FALSE, out.width="70%", warning=FALSE, message=FALSE}
 ggplot(data = wbdata, aes(x = Year, y = Exportsofgoodsandservices)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "#8E2C90") + 
  labs(
    title = "Foriegn Direct Investment over the Year",
    subtitle = "Foriegn Direct Investment, 1960 - 2018",
    x = "Width (Years)",
    y = "Height (Dollar)"
  ) + geom_smooth(method = "lm", color = "#8E2C90", se = FALSE) +
  geom_point(mapping = aes(y = Foreigndirectinvestment), color = "#E48957") +
  labs(subtitle = "") + 
  geom_segment(mapping = aes(xend = Year, yend = Foreigndirectinvestment
), color = "#E48957", alpha = 0.4) +
  labs(subtitle = "")

```

## Transport Services

```{r vis-res-2, echo=FALSE, out.width="70%"}
ggplot(data = wbdata, aes(x = Year, y = transportservices)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "#8E2C90") + 
  labs(
    title = "Transport Services",
    subtitle = "Transport Servicess, 1960 - 2018",
    x = "Width (Years)",
    y = "Height (Number)"
  ) +
  geom_smooth(method = "lm", color = "#8E2C90", se = FALSE) +
  geom_point(mapping = aes(y = transportservices), color = "#E48957") +
  labs(subtitle = "")

```


## Analysis of Export Of IT Services

```{r height-width-plot, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(data = wbdata, aes(x = Year, y = ICTservices)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "#8E2C90") + 
  labs(
    title = "Year vs. Export of ICT Services",
    subtitle = "Export Of IT Servoces, 1960 - 2018",
    x = "Width (Years)",
    y = "Height (Number)"
  )

```
## Analysis of Export Of IT Services

It has been analyzed from the data that export data, ICT services and foriegn investment have increased over the period of time. Which implies that economy and growth is increasing year by year
