---
title: 'A01: GGPLOT2'
author: Naveen
date: '2021-05-20'
slug: a01-ggplot2
categories:
  - ggplot2
tags: []
---

## Categorical  and Numerical visualization Part 1 


* First bullet point under part 1 

* Second bullet point under part 1



## Categorical  and Numerical visualization Part 2 

* First bullet point under part 2 

* Second bullet point under part 2



## Numerical  data visualization

```{r message=FALSE, echo= FALSE}

library(tidyverse)
library(openintro)


loans <- loans_full_schema %>%
  select(loan_amount, interest_rate, term, grade, 
         state, annual_income, homeownership, debt_to_income)




ggplot(loans, aes(x = loan_amount, fill = homeownership)) + 
  geom_histogram(binwidth = 5000) +
  labs(
    x = "Loan amount ($)",
    y = "Frequency",
    title = "Amounts of Lending Club loans"
  ) +
  facet_wrap(~ homeownership, nrow = 3)

ggplot(loans, aes(x = loan_amount)) +
  geom_histogram(binwidth = 5000) +
  labs(
    x = "Loan amount ($)",
    y = "Frequency",
    title = "Amounts of Lending Club loans"
  )

```




## Categorical data visualization

```{r message=FALSE, echo= FALSE}
library(openintro)
library(ggplot2) 

ggplot(loans, aes(y = homeownership,
                  fill = grade)) +
  geom_bar(position = "fill") +
  labs(
    x = "Proportion",
    y = "Homeownership",
    fill = "Grade",
    title = "Grades of Lending Club loans",
    subtitle = "and homeownership of lendee"
  )


ggplot(loans, aes(x = loan_amount, fill = homeownership)) + 
  geom_histogram(binwidth = 5000) +
  labs(
    x = "Loan amount ($)",
    y = "Frequency",
    title = "Amounts of Lending Club loans"
  ) +
  facet_wrap(~ homeownership, nrow = 3)
```


The main interesting thing about the GGPPLOT was how easy it is to display the complex data on the webpages. 

Contrary to that, I find issues to render the graphs to the website.
